---
title: "P8105 HW 1"
author: "Emily Potts (enp2116)"
date: "2022-09-24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

# Problem 1

```{r, echo=FALSE}
data("penguins", package = "palmerpenguins")
```

* The `penguins` dataset includes the variables: `r names(penguins)`. The variable of species has values: `r levels(penguins$species)`. The variable of flipper_length_mm has values such as `r head(penguins$flipper_length_mm)` mm and bill_length_mm has values such as `r head(penguins$bill_length_mm)` mm.

* The `penguins` dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* Across all penguin species, the mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r, echo = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species, )) + geom_point() + xlab("Bill Length (mm)") + ylab("Flipper Length (mm)") + ggtitle("Scatterplot of Bill Length vs. Flipper Length by Species")
ggsave("penguins_scatterplot.pdf", height = 4, width = 6)
```



# Problem 2


