---
title: "P8105 HW 1"
author: "Emily Potts (enp2116)"
date: "2022-09-24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

# Problem 1

First, I'm loading the `penguins` dataset from the PalmerPenguins package.
```{r}
data("penguins", package = "palmerpenguins")
```

* The `penguins` dataset includes the variables: `r names(penguins)`. The variable of species has values: `r levels(penguins$species)`. The variable of flipper_length_mm has values such as `r head(penguins$flipper_length_mm)` mm and bill_length_mm has values such as `r head(penguins$bill_length_mm)` mm.

* The `penguins` dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns, indicating we have data on `r nrow(penguins)` different penguins and are measuring at most `r ncol(penguins)` different traits in each penguin.

* Across all penguin species, the mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

Using ggplot, I'm creating a labeled scatterplot of flipper_length_mm (y) vs bill_length_mm (x), color-coded by species.
```{r, echo = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species, )) + geom_point() + xlab("Bill Length (mm)") + ylab("Flipper Length (mm)") + ggtitle("Scatterplot of Bill Length vs. Flipper Length by Species")
ggsave("penguins_scatterplot.pdf", height = 4, width = 6)
```


# Problem 2

I'm creating a dataframe with a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”.
```{r}
df = tibble(
  random_samp = rnorm(10, mean = 0, sd = 1),
  vec_logical = (random_samp > 0),
  vec_char = c("a", "b", "c", "d", "e", "f", "h", "i", "j", "k"),
  vec_factor = factor(c("single", "married", "married", "single", "divorced", "divorced", "single", "married", "married", "divorced"), levels = c("single", "married", "divorced"))
)
str(df)
```

R allows us to take the mean of the random sample and of the logical vector, counting TRUE as 1 and FALSE as FALSE. 
```{r}
mean(pull(df, random_samp))
mean(pull(df, vec_logical))
```

R does not allow us to take the mean of the character vector or of the factor vector. 
```{r}
mean(pull(df, vec_char))
mean(pull(df, vec_factor))
```


This is code that applies the as.numeric function to the logical, character, and factor variables 
```{r, results = FALSE, warning = FALSE}
as.numeric(pull(df, vec_logical))
as.numeric(pull(df, vec_char))
as.numeric(pull(df, vec_factor))
```

* When we make the logical vector numeric, we get 1s for TRUE and 0s for FALSE. This means we can interpret a mean of 0.5 to indicate TRUE occurs just as much as FALSE in the random sample.

* When we make the character vector numeric, we get a string of NAs, which explain why we could not generate a mean.

* When we make the factor vector numeric, we have our factors labelled as 1, 2, and 3 in the order that they were imposed in the creation of the dataframe. However, it makes sense that R does not automatically count the factors as numbers in generating a mean, since number assignment is arbitrary.
